\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliography}

%\bibitem{label} Autoren: Titel, Verlag, \url{http://...}, Datum.

\bibitem{educhain-proposal} Christian Killer, Eder Scheid, Bruno Rodrigues, Geetha Parangi, Burkhard Stiller: Swiss EDUCHAIN
Project Proposal. Project Proposal. Universita\"t Zurich, Communication Systems Group, Department of Informatics, Zu\"rich, Switzerland, July 2019.

\bibitem{educhain-architecture} Jerinas Gresch, Bruno Rodrigues, Eder Scheid, Sali Kanhere, Burhard Stiller: The Proposal of
a Blockchain-based Architecture for Transparent Certificate Handling. Business Information Systems
(BIS) 2018 International Workshops, Berlin, Germany, July 18, 2018, Revised Papers,
pp.185-196.

\bibitem{mit-digital-diploma} MIT Registrars Office. Digital Diploma. Available [Online] \url{http://bit.ly/mit-registrar/}, Accessed
August 12, 2019


\bibitem{mit-digital-diploma-faq} MIT Registrars Office. Digital Diploma Program FAQs. Available [Online] \url{https://bit.ly/2JYw4zT},
Accessed August 12, 2019


\bibitem{unic-certificates} University of Nicosia. Academic certificates on the Blockchain. Available [Online]: \url{https://bit.ly/2I5G3mj}, Accessed August 12, 2019

\bibitem{polkadot} Gavin Wood. Polkadot: Vision for a Heterogeneous Multi-Chain Framework. November 2016,
Available [Online]: \url{https://polkadot.network/PolkaDotPaper.pdf}, Accessed August 12, 2019

\bibitem{ethereum} Ethereum, Available at \url{https://ethereum.org}, Accessed August 12, 2019

\bibitem{corda} Corda, Available at \url{https://corda.net}, Accessed August 12, 2019

\bibitem{hyperledger-wiki} Hyperledger Wiki. Accessed Aug 15, 2019. Available [Online]: \url{https://wiki.HL.org/}

\bibitem{hyperledger-fabric-wiki} Hyperledger Fabric Wiki. Accessed Aug 15, 2019. Available [Online]: \url{https://wiki.hyperledger.org/display/fabric/}

\bibitem{hyperledger-indy-wiki} Hyperledger Indy Wiki. Accessed Aug 15, 2019. Available [Online]: \url{https://wiki.hyperledger.org/display/indy/}

\bibitem{sovrin} Sovrin Foundation. Accessed Aug 15, 2019. Available [Online]: \url{https://sovrin.org/}

\bibitem{musee} N. M. Musee, An Academic Certification Verification System Based on Cloud Computing Environment.
PhD dissertation, University of Nairobi, 2015

\bibitem{wicked-problem} H. Park and A. Craddock. Diploma Mills: 9 Strategies for Tackling One of Higher Education's
MostWicked Problems. Accessed Aug 15, 2019. Available [Online]: \url{https://bit.ly/2DoEeyu}

\bibitem{blockcerts} Google Play Store. Blockcerts Wallet. Accessed Aug 15, 2019. Available [Online]: \url{http://bit.ly/blockcerts-wallet}

\bibitem{cardano-diplomas} A. Castor. Cardano Blockchain's First Use Case: Proof of University Diplomas in Greece.
Accessed Aug 15, 2019. Available [Online]: \url{https://bit.ly/2DVsrYt}

\bibitem{mit-trust} Trust::Data Consortium - An initiative of MIT Connection Science. Accessed Aug 15, 2019. Available
[Online]: \url{https://www.trust.mit.edu/about}

\end{thebibliography}

